Characterize the fetal kidney reference from the kidney cell atlas

### 2024-11-04 analyses/cell-type-wilms-tumor-06/notebook_template/00b_characterize_fetal_kidney_reference_Stewart.Rmd
textual changes

The aim is to characterize the human fetal kidney from the kidney cell atlas.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1]
The rds data can be download using the download link https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds
The azimuth compatible reference has been downloaded and created in the `R script` `download-and-create-fetal-kidney-ref.R`

@@

Load required packages in the following chunk, if needed.
Do not install packages here; only load them with the `library()` function.

```{r packages, message=FALSE, warning=FALSE}
library("Seurat")
library(Azimuth)
library(SCpubr)
library(tidyverse)
library(patchwork)

>>>>

The aim is to characterize the human fetal kidney from the kidney cell atlas.
You can find more about the human kidney atlas here: https://www.kidneycellatlas.org/ [1]
The rds data can be download using the download link https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds
The reference was been downloaded and created in the script `scripts/prepare-fetal-references.R`.

@@

```{r packages, message=FALSE, warning=FALSE}
library(Seurat)
library(Azimuth)
library(SCpubr)
library(tidyverse)
library(patchwork)
